Simulated observations of young protoplanetary discs

### 2013-01-21 paper.tex
figures pretty much sorted

\begin{figure*}
 \includegraphics[width=168mm]{Figures/sim/imageHCOp_1-0_30deg_composite_all.eps}
 \label{h2co_all}
 \caption{HCO$^+$ 1-0 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
\end{figure*}

@@

\begin{figure}
 \includegraphics[width=54mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_PV_centre.eps}

 \caption{OCS 28-29 pv diagram simulated for ALMA most extended configuration}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_contSub.eps}

 \caption{OCS 28-29 integrated intesity simulated for ALMA most extended configuration}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/casa_HCOp_spectra_40_AUsplit.eps}

 \caption{HCO$^+$ 1-0 30 deg spectra at Y=0, X=+40AU (bottom), 0AU (middle) and -40AU (Top)}
\end{figure}

\begin{figure}
 \includegraphics[width=54mm]{Figures/sim/casa_imageC17O_3-2_30deg_composite_ALMAwidth_dirty_PV_centre.eps}

 \caption{C$^{17}$O 3-2 30 deg PV through centre simulated for ALMA most extended configuration}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/casa_C17O_3-2_mom0.eps}

 \caption{C$^{17}$O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/casa_C17O_spectra_20AUsplit.eps}

 \caption{C$^{17}$O 1-0 30 deg spectra at Y=0, X=+20AU (bottom), 0AU (middle) and -20AU (Top)}
\end{figure}

\begin{figure}
 \includegraphics[width=63mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_PV_centre.eps}

 \caption{HCO$^+$ 1-0 30 deg PV through centre simulated for ALMA most extended configuration}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_contSub.eps}

 \caption{HCO$^+$ 1-0 30 deg integrated intensity simulated for ALMA most extended configuration}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/casa_OCS_spectra_10AUsplit.eps}

 \caption{OCS 28-27 30 deg spectra at Y=0, X=+10AU (bottom), 0AU (middle) and -10AU (Top)}
\end{figure}

@@

Figures showing different inclinations {\bf (will redo these for compound images soon)}
\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_contSub.eps}

 \caption{C18O 3-2 15 deg Continuum subtracted mom0}
\end{figure}

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.eps}
%
% \caption{C18O 3-2 15 deg mom1map}
%\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_PV_centre.eps}

 \caption{C18O 3-2 PV 15 deg through centre}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_contSub.eps}

 \caption{C18O 3-2  30 deg Continuum subtracted mom0}
\end{figure}

@@

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_PV_centre.eps}

 \caption{C18O 3-2 30 deg PV through centre}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_contSub.eps}

 \caption{C18O 3-2 45 deg Continuum subtracted mom0}
\end{figure}

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.eps}
%
% \caption{C18O 3-2 45 deg mom1map}
%\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_PV_centre.eps}

 \caption{C18O 3-2 45 deg PV through centre}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_contSub.eps}

 \caption{C18O 3-2 60 deg Continuum subtracted mom0}
\end{figure}

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.eps}
%
% \caption{C18O 3-2 60 deg mom1map}
%\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_PV_centre.eps}

 \caption{C18O 3-2 60 deg PV through centre}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_contSub.eps}

 \caption{C18O 3-2 75 deg Continuum subtracted mom0}
\end{figure}

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.eps}
%
% \caption{C18O 3-2 75 deg mom1map}
%\end{figure}

\begin{figure}
%  \showthe\columnwidth % Use this to determine the width of the figure.
  \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_PV_centre.eps}
  \caption{C18O 3-2 75 deg PV through centre}
\end{figure}

>>>>

\begin{figure*}
 \includegraphics[width=168mm]{Figures/sim/imageHCOp_1-0_30deg_composite_all.eps}
 \label{hco+_all}
 \caption{HCO$^+$ 1-0 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
\end{figure*}

@@

%\begin{figure}
%\includegraphics[width=54mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_PV_centre.eps}
% \caption{OCS 28-29 pv diagram simulated for ALMA most extended configuration}
%\end{figure}

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/casa_OCS_26-25_30deg_contSub.eps}
%
% \caption{OCS 28-29 integrated intesity simulated for ALMA most extended configuration, contours %starting at 3$\sigma$ and increasing in intervals of 3$\sigma$}
%\end{figure}
%
%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/casa_H2CO_404-303_30deg_contSub.eps}
%
% \caption{H$_2$CO 4$_{04}$-3$_{03}$ integrated intesity simulated for ALMA most extended configuration, %contours starting at 5$\sigma$ and increasing in intervals of 5$\sigma$}
%\end{figure}
%
%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/casa_HCOp_spectra_40_AUsplit.eps}
%
% \caption{HCO$^+$ 1-0 30 deg spectra at Y=0, X=+40AU (bottom), 0AU (middle) and -40AU (Top)}
%\end{figure}

\begin{figure*}
 \includegraphics[width=168mm]{Figures/sim/channel_map-1.eps} 
 \label{h2co_chanmap}
 \caption{H$_2$CO 4$_{04}$-3$_{03}$ channel maps as simulated by CASA. H$_2$CO line in contours starting at 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$ (absorption in red, emission in blue). Overlaid on the continuum emission. Each map integrates over 2.4 km$\,$s$^{-1}$ with the top left from -10.8 to -8.4 km$\,$s$^{-1}$ to the bottom left ranging from 8.4 to 10.8 km$\,$s$^{-1}$}
\end{figure*}

%\begin{figure}
%\includegraphics[width=54mm]{Figures/sim/casa_imageC17O_3-2_30deg_composite_ALMAwidth_dirty_PV_centre.eps}
% \caption{C$^{17}$O 3-2 30 deg PV through centre simulated for ALMA most extended configuration}
%\end{figure}

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/casa_C17O_3-2_30deg_contSub.eps}
%
% \caption{C$^{17}$O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration, %contours starting at 3$\sigma$ and increasing in intervals of 3$\sigma$}
%\end{figure}

\begin{figure*}
 \includegraphics[width=168mm]{Figures/sim/casa_all_30deg_contSub.eps}

 \caption{C$^{17}$O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration, contours starting at 3$\sigma$ and increasing in intervals of 3$\sigma$}
\end{figure*}

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/casa_C17O_spectra_20AUsplit.eps}
%
% \caption{C$^{17}$O 1-0 30 deg spectra at Y=0, X=+20AU (bottom), 0AU (middle) and -20AU (Top)}
%\end{figure}

%\begin{figure}
%\includegraphics[width=63mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_PV_centre.eps}
% \caption{HCO$^+$ 1-0 30 deg PV through centre simulated for ALMA most extended configuration}
%\end{figure}

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/casa_HCOp_3-2_30deg_contSub.eps}
%
% \caption{HCO$^+$ 3-2 30 deg integrated intensity simulated for ALMA most extended configuration. %Contours start at 3$\sigma$ and increase in steps of 3$\sigma$}
%\end{figure}

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/casa_H2CO_404-303_30deg_contSub.eps}
%
% \caption{H$_2$CO 404-303 30 deg integrated intensity simulated for ALMA most extended configuration. Contours start at 5$\sigma$ and increase in steps of 10$\sigma$}
%\end{figure}

\begin{figure*}
 \includegraphics[width=198mm]{Figures/sim/casa_all_30deg_PV_rotCurve.eps}

 \caption{PVs with model rotation curve}
\end{figure*}

\begin{figure*}
 \includegraphics[width=168mm]{Figures/sim/casa_all_spectra.eps}

 \caption{Spectra, H$_2$CO 20AU split, C$^{17}$O 28AU split, OCS 10AU split, HCO$^+$ 38AU split}
\end{figure*}

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/casa_OCS_spectra_10AUsplit.eps}
%
% \caption{OCS 28-27 30 deg spectra at Y=0, X=+10AU (bottom), 0AU (middle) and -10AU (Top)}
%\end{figure}

@@

Figures showing different inclinations 
\begin{figure*}
 \includegraphics[width=198mm]{Figures/sim/imageC17O_3-2_15deg_all.eps}

 \caption{C$^{17}$O 3-2 15 deg Continuum subtracted mom0}
\end{figure*}

\begin{figure*}
 \includegraphics[width=198mm]{Figures/sim/imageC17O_3-2_45deg_all.eps}

 \caption{C$^{17}$O 3-2 45 deg Continuum subtracted mom0}
\end{figure*}

\begin{figure*}
 \includegraphics[width=198mm]{Figures/sim/imageC17O_3-2_75deg_all.eps}

 \caption{C$^{17}$O 3-2 75 deg Continuum subtracted mom0}
\end{figure*}

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_contSub.eps}
%
% \caption{C18O 3-2 15 deg Continuum subtracted mom0}
%\end{figure}
%
%%\begin{figure}
%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.eps}
%%
%% \caption{C18O 3-2 15 deg mom1map}
%%\end{figure}
%
%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_PV_centre.eps}
%
% \caption{C18O 3-2 PV 15 deg through centre}
%\end{figure}
%
%
%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_contSub.eps}
%
% \caption{C18O 3-2  30 deg Continuum subtracted mom0}
%\end{figure}

@@

%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_PV_centre.eps}
%
% \caption{C18O 3-2 30 deg PV through centre}
%\end{figure}
%
%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_contSub.eps}
%
% \caption{C18O 3-2 45 deg Continuum subtracted mom0}
%\end{figure}
%
%%\begin{figure}
%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.eps}
%%
%% \caption{C18O 3-2 45 deg mom1map}
%%\end{figure}
%
%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_PV_centre.eps}
%
% \caption{C18O 3-2 45 deg PV through centre}
%\end{figure}
%
%
%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_contSub.eps}
%
% \caption{C18O 3-2 60 deg Continuum subtracted mom0}
%\end{figure}
%
%%\begin{figure}
%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.eps}
%%
%% \caption{C18O 3-2 60 deg mom1map}
%%\end{figure}
%
%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_PV_centre.eps}
%
% \caption{C18O 3-2 60 deg PV through centre}
%\end{figure}
%
%\begin{figure}
% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_contSub.eps}
%
% \caption{C18O 3-2 75 deg Continuum subtracted mom0}
%\end{figure}
%
%%\begin{figure}
%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.eps}
%%
%% \caption{C18O 3-2 75 deg mom1map}
%%\end{figure}
%
%\begin{figure}
%%  \showthe\columnwidth % Use this to determine the width of the figure.
%  \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_PV_centre.eps}
%  \caption{C18O 3-2 75 deg PV through centre}
%\end{figure}
